Supplementary Figure 1f

### 2017-11-20 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

markdown <- p +
  geom_linerange(
    data = stats,
    aes(
      x = Time,
      colour = `Cell line`,
      ymin = min,
      ymax = max
    ), 
    position = position_dodge(width = 1),
    show.legend = FALSE
  ) + 
  geom_point(
    data = stats,
    aes(
      x = Time, 
      y = median,
      group = `Cell line`,
      colour = `Cell line`
    ), 
    position = position_dodge(width = 1),
    show.legend = TRUE
  ) + 
  guides(
    colour = guide_legend(title = "Cell line", override.aes = list(size = 3))
  )

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = Time,
      colour = `Cell line`,
      ymin = min,
      ymax = max
    ), 
    position = position_dodge(width = 1),
    lwd = 0.1,
    show.legend = FALSE
  ) + 
  geom_point(
    data = stats,
    aes(
      x = Time, 
      y = median,
      group = `Cell line`,
      colour = `Cell line`
    ), 
    size = 0.25,
    position = position_dodge(width = 1),
    show.legend = TRUE
  ) + 
  guides(
    colour = guide_legend(title = "Cell line", override.aes = list(size = 2))
  )

figure <- plotPDF(pdf)

path <- "~/GitHub/miR34a_asRNA_project/inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.pdf"
# ggsave(
#   plot = figure,
#   filename = path,
#   device = cairo_pdf,
#   height = 60,
#   width = 83,
#   units = "mm"
# )
```

>>>>

markdown <- p +
  geom_linerange(
    data = stats,
    aes(
      x = Time,
      colour = `Cell line`,
      ymin = min,
      ymax = max
    ), 
    position = position_dodge(width = 1),
    show.legend = FALSE
  ) + 
  geom_point(
    data = stats,
    aes(
      x = Time, 
      y = median,
      group = `Cell line`,
      colour = `Cell line`
    ), 
    position = position_dodge(width = 1),
    show.legend = TRUE
  ) + 
  guides(
    colour = guide_legend(
      title = "Cell line", 
      override.aes = list(size = 3)
    )
  )

@@

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = Time,
      colour = `Cell line`,
      ymin = min,
      ymax = max
    ), 
    position = position_dodge(width = 1),
    lwd = 0.1,
    show.legend = FALSE
  ) + 
  geom_point(
    data = stats,
    aes(
      x = Time, 
      y = median,
      group = `Cell line`,
      colour = `Cell line`
    ), 
    size = 0.25,
    position = position_dodge(width = 1),
    show.legend = TRUE
  ) + 
  guides(
    colour = guide_legend(
      title = "Cell line", 
      override.aes = list(size = 2)
    )
  )

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.pdf"

ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 83,
  units = "mm"
)
```

### 2017-11-20 inst/transcript_stability/transcript_stability.Rmd
a whole lot of name changes to paths because of issue #2 and a function that now maps figures to files

p <- ggplot(data = NULL)+
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Treatment (hours)",
    title = "miR34a asRNA and HG stability"
  ) +
  guides(color = guide_legend(title = "Gene", override.aes = list(size = 3)))

@@

#ggsave(
#  plot = figure, 
#  filename = path, 
#  device = cairo_pdf, 
#  height = 60,
#  width = 83,
#  units = "mm"
#)
```

>>>>

p <- ggplot(data = NULL)+
  scale_y_continuous("\u0394\u0394Ct") +
  labs(
    x = "Treatment (hours)",
    title = "miR34a asRNA and HG stability"
  ) +
  guides(
    color = guide_legend(
      title = "Gene", 
      override.aes = list(size = 3)
    )
  )

@@

ggsave(
 plot = figure,
 filename = path,
 device = cairo_pdf,
 height = 60,
 width = 83,
 units = "mm"
)
```
